Attentional Object Detection\\ Report for CS 294-67 Sequential Decisions

### 2012-01-21 writeups/rl_class/report.tex
ported rl_detection writeups in

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage[top=1in, bottom=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{subfig}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false,citecolor=red,linkcolor=blue]{hyperref}

@@

\title{Attentional Object Detection: A Proposal}
\author{Sergey Karayev}
\date{updated: 22 April 2011}

@@

\begin{abstract}
This document tracks the development of ideas for efficient object detection using the idea of attention: a sequential process of looking for something somewhere.
We follow the Deformable Part Model approach to object detection and extend it in several ways, mostly focusing on the role of context, toward the goal of Anytime detection performance.
I expect a submission to NIPS'11 to be whittled down from the text and results here.
\end{abstract}

\tableofcontents
\newpage

\input{introduction.tex}
\input{related_work.tex}
\input{evaluation.tex}
\input{our_approach.tex}
\input{discretization_and_featurization.tex}
\input{ideas.tex}
\input{results.tex}

>>>>

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage[top=1in, bottom=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{subfig}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false,citecolor=red,linkcolor=blue]{hyperref}

@@

\title{Attentional Object Detection\\
Report for CS 294-67 Sequential Decisions}
\author{Sergey Karayev}
\date{13 May 2011}

@@

\begin{abstract}
  Multi-class object detection in cluttered natural scenes is a long-standing open problem in computer vision. Currently best-performing approaches are computationally expensive. We seek to ameliorate this through replacing exhaustive and unprioritized search with a sequential decision process.
\end{abstract}

\input{introduction.tex}
\input{related_work.tex}
\input{evaluation.tex}
\input{our_approach.tex}
\input{experiments.tex}
